Epilepsy GLMM example

### 2023-02-14 src/epil/epil.Rmd
Plots of lognormconsts and difference between epil and naomi-simple Laplace implementations

laplace_x <- lapply(1:nrow(index_controller), safe_xi_laplace_marginal, opt_theta = opt_theta, finegrid = fine_grid)

laplace_beta_summary <- lapply(head(laplace_x, n = dat$K), function(result) summary(result$quad)$summarytable) %>%
  bind_rows()

rownames(laplace_beta_summary) <- paste0("beta[", 1:dat$K, "]")
```

@@

adam12 <- as.vector(t(laplace_beta_summary[1:6, 1:2]))

>>>>

laplace_x <- lapply(1:nrow(index_controller), safe_xi_laplace_marginal, opt_theta = opt_theta, finegrid = fine_grid)
```

Test that all the normalising constants calculated are constant, and equal to that obtained by `aghq`:

```{r}
aghq_lognormconst <- fit11$normalized_posterior$lognormconst

lognormconsts <- purrr::map(laplace_x, function(x) x$quad$normalized_posterior$lognormconst)

data.frame(lognormconst = unlist(lognormconsts)) %>%
  ggplot(aes(y = lognormconst, x = 1:length(lognormconst))) +
    geom_point(alpha = 0.3) +
    geom_hline(yintercept = aghq_lognormconst, linetype = "dashed") +
    theme_minimal() +
    labs(
      title = "Comparison of log normalising constants",
      y = "Log normalising constant", x = "Latent field index"
    )
```

The differences between this old approach, and the newer approach used in `naomi-simple` are:

1. Use of the `map` argument to fix theta to modal values. Which is useful for producing a `TMB` objective `obj_fixed_theta`
2. Passing `obj_fixed_theta` directly into `aghq::aghq` to do the selection of the points (here `k = 3`), integration and computation of the posterior with `aghq::compute_pdf_and_cdf`

@@

laplace_beta_summary <- lapply(head(laplace_x, n = dat$K), function(result) summary(result$quad)$summarytable) %>% bind_rows()
rownames(laplace_beta_summary) <- paste0("beta[", 1:dat$K, "]")
adam12 <- as.vector(t(laplace_beta_summary[1:6, 1:2]))
